\begin{abstract}
Smart contracts are programs that execute autonomously on blockchains. Their key envisioned uses (e.g., financial instruments) require them to consume data from outside the blockchain (e.g., stock quotes). Trustworthy {\em data feeds} that can support a broad range of data requests will thus be critical to smart contract ecosystems. 

	We present an authenticated data feed system called {\em Town Crier} (TC). TC acts as a bridge between existing web sites, which are already commonly trusted for non-blockchain applications, and smart contracts. It combines a blockchain front end with a trusted hardware back end to scrape HTTPS-enabled websites and serve source-authenticated data to relying smart contracts. TC also supports confidentiality: It enables private data requests with encrypted parameters, as well as secure use of user credentials to scrape access-controlled online data sources.
	
	We describe TC's design principles and architecture and report on an implementation that uses Intel's recently introduced Software Guard Extensions (SGX) to furnish data to the Ethereum smart contract system. We formally model TC and  define and prove its basic security properties in the Universal Composibility (UC) framework. Our results include definitions and techniques of general interest relating to resource consumption (Ethereum's ``gas'' fee system) and TCB minimization. We also report on experiments with three example applications. 
	
	We plan to launch TC soon as an online public service.
\end{abstract}
