\section{Related Work}
\label{sec:related}

Virtual Notary~\cite{VN:2013,VN:2016} is the first online data attestation service of which we are aware that verifies and digitally signs any of a range of user-requested ``factoids'' (web page contents, stock prices, etc., etc.) potentially suitable for smart contracts. It predates and does not at present interface with Ethereum.

Several data feeds are deployed today specifically for smart contract systems such as Ethereum. Examples include PriceFeed~\cite{PriceFeed:2016} and Oraclize.it~\cite{Oraclize:2016}. The latter beneficially achieves distributed trust by using a second service called TLSnotary~\cite{TLSnotary}, which digitally signs webpages. As a result, however, unlike \tc, which can flexibly tailor datagrams, Oraclize.it is constrained to delivering data as served in a web session or API call; verbose sources can thus result in superfluous data and inflated gas costs for datagrams. Additionally, this approach cannot support private or custom datagrams. 

Existing data feed services ultimately rely on the reputations and operational security of typically small providers and integrated services (e.g., TLSnotary) to ensure data authenticity. 
To address this problem, systems such as SchellingCoin~\cite{schellingcoin} and Augur~\cite{augur} rely on mechanisms such as prediction markets to decentralize trust. Prediction markets often rely on human input, though, constraining their scope. They have not yet seen widespread use in cryptocurrencies. 

Despite an active developer community, research community exploration of smart contracts has been very limited to date. Work includes off-chain contract execution for confidentiality~\cite{hawk}, and, more tangentially, exploration of e.g., randomness sources in~\cite{bonneau2015bitcoin}. The only exploration relating to data feeds of which we're aware is discussion of their use for (criminal) applications in~\cite{gyges}.

SGX is similarly in its infancy.
While a Windows SDK~\cite{sgxsdk} and programming manual~\cite{sgxmanual} have just been released, a number of pre-release papers have already explored SGX, e.g., \cite{VC3,7163052,anati2013innovative,McKeen:2013jv,Phegade:2013km}. Researchers have demonstrated applications including enclave execution of legacy (non-SGX) code~\cite{haven} and use of SGX in a distributed setting for map-reduce computations~\cite{VC3}. Several works have exposed shortcomings of the security model for SGX~\cite{sgxexplained,sgxsok,shihardwaretalk}, including side-channel attacks and other attacks against enclave state. 


